The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-03-21 ms.Rmd
setting up bibliography & MEE-style citations

---
title: "The `zoon` R package for reproducible and shareable species distribution modelling"
author: "Nick Golding, Tom August, Tim C.D. Lucas, Emiel Van Loon & Greg McInerny"
date: "4 March 2016"
output: 
  pdf_document:
    fig_caption: yes
---

@@

<!-- The Problem -->
Reproducibility crisis in species distribution modelling (SDM).
Difficult for new SDM users to access latest methods.
Difficult for anyone to compare methods effectively. 
Equally difficult for methods developers to disseminate their advances.

@@

>>>>

---
title: "The `zoon` R package for reproducible and shareable species distribution modelling"
author: "Nick Golding, Tom August, Tim C.D. Lucas, Emiel Van Loon & Greg McInerny"
date: "21 March 2016"
bibliography: zoon_app.bib
csl: mee.csl
output: 
  pdf_document:
    fig_caption: yes
---

@@

<!-- The Problem -->

SDM boom & growth of methods literature [@Barbosa2015]

Reproducibility crisis in species distribution modelling (SDM).

Difficult for new SDM users to access latest methods.

Difficult for anyone to compare methods effectively.

Equally difficult for methods developers to disseminate their advances.

@@

### References
